---
title: "Working with Tuning Parameters"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Working with Tuning Parameters}
output:
  knitr:::html_vignette:
    toc: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
  )
options(digits = 3)
library(dials)
library(rpart)
```

# Tuning Parameters 

Some statistical and machine learning models contain _tuning parameters_ (also known as _hyperparameters_), which are parameters that cannot be directly estimated by the model. An example would be the number of neighbors in a _K_-nearest neighbors model. To determine reasonable values of these elements, some indirect method is used such as resampling or profile likelihood. Search methods, such as genetic algorithms or Bayesian search can also be used to [determine good values](https://github.com/topepo/Optimization-Methods-for-Tuning-Predictive-Models). 

In any case, some information is needed to create a grid or to validate whether a candidate value is appropriate (i.e. neighbors should be a positive integer). `dials` is designed to:

 * Create an easy to use framework for describing and querying tuning parameters. this can include getting sequences or random tuning values, validating current values, transforming parameters, and other tasks.
 * Standardize the names of different parameters. Different packages in R use different argument names for the same quantities. `dials` proposes some standardized names so that the user doesn't need to memorize the syntactical minutiae of every package. 
 * Work with the [`parsnip`](https://topepo.github.io/parsnip/)  package which is a modern attempt to standardize the interfaces for specific models across R packages and computational engines. 
 * Adhere to [tidy principals](https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html). 

The main type of objects in `dials` have class `param`.


change `units` to `hidden_units` and `weight_decay` to `regularization`

# `param` Objects

`param` objects contain information about possible values, ranges, types, and other aspects. There are two main subclasses related to the type of variable. Double and integer valued data have the subclass "quant_param" while character and logicals have "qual_param." There are some common elements for each:

 * Labels are strings that describe the parameter (e.g. "Number of Components")
 * Defaults are optional single values that can be set when one non-random value is requested. 

Otherwise, the information contained in `param` objects are different for different data types. 


# Numeric Parameters

An example of a numeric tuning parameter is the cost-complexity parameter of CART trees, other wise known as $C_p$. The parameter object in `dials` is:

```{r cp}
library(dials)
Cp
```

Note that this parameter is handled in log units and the default range of values is between `10^-10$ and 0.1. The range of possible values can be returned and changed based on some utility functions. We'll use the pipe operator here:

```{r cp-range}
library(tidymodels)
Cp %>% range_get()
Cp %>% range_set(c(-5, 1))
```

Values for this parameter can be obtained in a few different ways. To get a sequence of values that span the range: 

```{r cp-seq}
# Natural units:
Cp %>% value_seq(n = 4)
# Stay in the transformed space:
Cp %>% value_seq(n = 4, original = FALSE)
```

Random values can be sampled too. A random uniform distribution is used (between the range values). Since this parameter has a transformation associated with it, the values are simulated in the transformed scale and then returned in the natural units (although another `original` argument can be used here): 

```{r cp-sim}
set.seed(5473)
Cp %>% value_sample(n = 4)
```

For CART trees, there is a discrete set of values that exist for a given data set. It may be a good idea to assign these possible values to the object. We can get them by fitting an initial `rpart` model and then adding the values to the object. For `mtcars`, there are only three values:

```{r rpart, error=TRUE}
library(rpart)
cart_mod <- rpart(mpg ~ ., data = mtcars, control = rpart.control(cp = 0.000001))
cart_mod$cptable
cp_vals <- cart_mod$cptable[, "CP"]
# Ww should only keep values associated with at least one split:
cp_vals <- cp_vals[ cart_mod$cptable[, "nsplit"] > 0 ]
mtcars_cp <- Cp %>% value_set(cp_vals)
```

The error occurs because the values are not in the transformed scale:

```{r rpart-cp}
mtcars_cp <- Cp %>% value_set(log10(cp_vals))
mtcars_cp
```

Now, if we want a sequence or random sample, it uses the set values:

```{r rpart-cp-vals}
mtcars_cp %>% value_seq(2)
# Sampling specific values is done with replacement
mtcars_cp %>% 
  value_sample(20) %>% 
  table()
```


# Discrete Parameters



# Unknown Values


# Parameter Grids



