---
title: "Using Dials with Parsnip"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Using Dials with Parsnip}
output:
  knitr:::html_vignette:
    toc: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
  )
options(digits = 3)
library(dials)
library(parsnip)
```

[`parsnip`](https://tidymodels.github.io/parsnip) is a package in development that provides more unified interfaces to model functions. It has functions to create a _model specification_ that can be used to fit a particular model using different R packages (or by other means). these model specifications have main arguments for important tuning parameters.  For example, a minimal model specification is:

```{r bst-spec}
library(parsnip)
boost_tree(mode = "classification")
```

This particular model has a number of different arguments for tuning parameters:

```{r bst-str}
str(boost_tree)
```

If we know exactly what specific value of a parameter should be, it can be specified:

```{r bst-args}
boost_tree(mode = "classification", trees = 50, min_n = 5, sample_size = 3/4)
```

Note that :

 * These parameter names have identically named parameter objects in `dials`.
 * Like other `parsnip` functions, `boost_tree` can use different R packages to fit this model, in this case, `xgboost` and `C50`. Not all parameters to `boost_tree` are relevant to each of these specific models. 
 * Any parameters not specified in this call will use their model-specific defaults. 

What happens if you know that you want to optimize the value of a parameter but don't know what the value will be? In this case, the `parsnip` function `varying()` can be used as a placeholder. For example, `min_n` is conditional on the sample size of the training set, so we may not know a feasible value until be have the exact training or analysis set: 

```{r bst-vary}
mod_obj <- boost_tree(mode = "classification", trees = 50, min_n = varying(), sample_size = 3/4)
mod_obj
```

If some type of grid search is used, there is a simple function in `dials` can be used to update this parameter specification with candidate values. Let's create a small, random grid for these parameters. We will set the ranges for these parameters in-line when creating the grid:

```{r bst-grid}
library(tidymodels)
library(dials)

set.seed(1263)
bst_grid <- random_grid(
  trees %>%       range_set(c( 1,  50)), 
  min_n %>%       range_set(c( 2,  30)), 
  sample_size %>% range_set(c(20, 130)), 
  size = 3
)
bst_grid
```

We can use the `merge` function to combine these parameters with the model specification:

```{r bst-loop}
for(i in 1:nrow(bst_grid)) {
  print(merge(mod_obj, bst_grid[i, ]))
}
```
